Secure Composition of SPECTRE Variants

### 2023-10-29 prisc-spectre/prisc.tex
Minor changes to prisc

Some programming languages of today enjoy strong security guarantees that programmers want to have, such as the memory-safety guarantees given by the semantic analysis pass of a compiler for the Rust programming lanugage.
While programmers may expect that these guarantees hold even after translating their program to the target programming language, it has been shown that this expectation is false in the general case~\MK{cit constant time examples}.
Even correct compilers do not provide satisfactory guarantees and one has to resort to secure compilers~\cite{abate19,abate20,patrignani21} which preserve property satisfaction even when the compiled program is linked with arbitrary target-level code.

@@

\begin{definition}[Compatibility]
tbd
\MKin{todo}
\end{definition}

@@

Within the framework of recent work\MK{cit kruse et al (arxiv)}, this extended abstract aims to formalize the semantic effect of mitigation mechanisms for SPECTRE variants and investigate their compatibility with each other.

This work aims to investigate the compatibility, within the framework of recent work\MK{kruse et al}, of source-code instrumentation passes that insert SPECTRE mitigations. 
Moreover, the paper investigates not only security-preserving compilers, but also security-\textit{enforcing} compilers. 
Enforcements make no assumptions to the code of a source-level component\footnote{Although the source-level language may impose restrictions by means of a type-system that nonetheless provide security guarantees.}.
%% MK:
%% motivation lacking for why we do it for just SPECTRE
%% literally no explanation for spectre whatsoever

>>>>

Some programming languages of today enjoy strong security guarantees, such as the memory-safety guarantees given by the semantic analysis pass of a compiler for the Rust programming lanugage.
While programmers may expect that these guarantees hold even after translating their program to the target programming language, it has been shown that this expectation is false in the general case~\MK{cit constant time examples}.
Even correct compilers do not provide satisfactory guarantees and one has to resort to secure compilers~\cite{abate19,abate20,patrignani21} which preserve property satisfaction even when the compiled program is linked with arbitrary target-level code.

@@

\begin{definition}[Compatibility]
  Given languages $\src{S}$ and $\trg{T}$, a cross-language trace relation $\sim$ between traces of $\src{S}$ and $\trg{T}$, and a $\trg{T}-$level class of properties $\trg{\mathbb{C}}$.
  $\sim$ is compatible with $\trg{\mathbb{C}}$ iff for any $\trg{\Pi}\subseteq\trg{\mathbb{C}}$ it holds that $\tilde{\sigma}(\trg{\Pi})\subseteq\tilde{\sigma}(\trg{\mathbb{C}})$.

%Definition gwfσ {S I : Language}
%  (rel : Trace (Event S) -> Trace (Event I) -> Prop)
%  (C : Class (Event I)) :=
%    forall (Π : Hyperproperty (Event I)),
%      belongs_to (Event I) Π C ->
%      belongs_to (Event S) (σ~ rel Π) (σ~ rel C)
\end{definition}

@@

Within the framework of recent work\MK{cit kruse et al (arxiv)}, this extended abstract aims to formalize the semantic effect of mitigation mechanisms for SPECTRE variants and investigate their compatibility with each other.
%
%
%This work aims to investigate the compatibility, within the framework of recent work\MK{kruse et al}, of source-code instrumentation passes that insert SPECTRE mitigations. 
Moreover, the paper investigates not only security-preserving compilers, but also security-\textit{enforcing} compilers. 
Enforcements make no assumptions to the code of a source-level component\footnote{Although the source-level language may impose restrictions by means of a type-system that nonetheless provide security guarantees.}.
%% MK:
%% motivation lacking for why we do it for just SPECTRE
%% literally no explanation for spectre whatsoever
